---
title: "case_study"
author: "Pei Liu"
date: "2022-10-11"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

Today is a case study

# Get Data

```{r}
library(p8105.datasets)

data(nyc_airbnb)

nyc_airbnb = nyc_airbnb %>% 
  rename(borough = neighbourhood_group) %>% 
  mutate(stars = review_scores_location / 2)

head(nyc_airbnb)

```
# Brainstorm questions
- what variables are relevant to higher review / scores?
- what are the popular places to rent an air bnb?
- what portion of hosts / locations are private rooms vs entire apartments?
- what makes an air bnb more expensive?
```{r}
most_popular = 
  nyc_airbnb %>%
  group_by(neighbourhood, borough) %>%
  distinct() %>%
  summarize(n_obs = n()) %>%
  ungroup() %>% 
  group_by(borough) %>% 
  mutate(rank = min_rank(desc(n_obs))) %>% 
  filter(rank < 5) %>% 
  arrange(borough, n_obs)

most_popular
```

Let's look at price...
```{r}
nyc_airbnb %>% 
  group_by(borough, room_type) %>% 
  summarize(
    mean_price = mean(price, na.rm = TRUE)
  ) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = mean_price
  )

```

Look at price distributions
```{r}
nyc_airbnb %>% 
  filter(
    borough == "Manhattan", 
    price < 1000) %>% 
  ggplot(aes(x = price)) +
  geom_histogram() +
  facet_grid(. ~ room_type)
```

Price vs … rating?
```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  ggplot(aes(x = stars, y = price)) + 
  geom_point() +
  facet_grid(. ~ room_type)
```

Somewhat fancy boxplot!
```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  group_by(neighbourhood) %>% 
  summarize(mean_price = mean(price, na.rm = TRUE)) %>% 
  arrange(desc(mean_price))
```

```{r}
nyc_airbnb %>% 
  filter(
    borough == "Manhattan",
    room_type == "Entire home/apt") %>% 
  filter(price <= 1000) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) + 
  geom_boxplot() +
  coord_flip()
```
Price vs location
```{r}
nyc_airbnb %>% 
  filter(
    borough == "Manhattan",
    room_type == "Entire home/apt") %>% 
  filter(price <= 1000) %>% 
  sample_n(2000) %>% 
  ggplot(aes(x = lat, y = long, color = price)) + 
  geom_point(alpha = .5)
```

```{r}
library(leaflet)

pal <- colorNumeric("viridis", domain = c(0,1000))
nyc_airbnb %>% 
  filter(
    borough == "Manhattan",
    room_type == "Entire home/apt") %>% 
  filter(price <= 1000) %>% 
  sample_n(1000) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(~lat, ~long, color = ~pal(price))
    
```

